\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-05 MasterDefense/main.tex
New

\begin{frame}
    It has been proposed that this model actually discretized a five-dimension gauge theory with gauge group $SU(m)$, where 
    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
     \vspace{1em} % 图与文字之间的间距
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \hspace{0.05\textwidth}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \end{center}
    \pause
    After higgsing the scalar field, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification. 
\end{frame}
\begin{frame}
    \frametitle{Scattering Amplitudes from BCFW}
    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
    \end{equation*}
We only foucus on the following amplitudes:
\begin{equation*}
    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
\end{equation*}
here n can be any positive integer.
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}

>>>>

\begin{frame}
    It has been proposed that this model actually discretized \textcolor{red}{a five-dimension gauge theory} with gauge group $SU(m)$, where 
    only the fifth dimension are latticed. So it is an effective theory for 5d gauge theory.
     \vspace{1em} % 图与文字之间的间距
    \begin{center}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Moosed.jpeg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \hspace{0.05\textwidth}
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\linewidth]{Lattice.jpg} % ← 替换为你的图片文件名
        \par\vspace{0.5em}
    \end{minipage}
    \end{center}
    \pause
    After higgsing the scalar field, we can obtain a spectrum
    \begin{equation*}
        M_k^2=4g^2f_s^2\sin^2\left(\frac{\pi k}{N}\right)
    \end{equation*}
    This is precisely the \textcolor{red}{Kaluza-Klein} spectrum under $S^2$ compactification. 
\end{frame}
\begin{frame}
    \frametitle{Scattering Amplitudes from BCFW}
    For simplicity, we start from the two-site gauge theory with gauge fields $V_1$, $V_2$ and scalar fields $\Phi$, $\Phi^\dagger$.
    \begin{equation*}
        \mathcal{L}=-\frac{1}{2}\mathrm{Tr}(F_1)^2-\frac{1}{2}\mathrm{Tr}(F_2)^2+\mathrm{Tr}[(D_\mu\Phi)^\dagger(D^\mu\Phi)],
    \end{equation*}
We only foucus on the following amplitudes:
\begin{equation*}
    \textcolor{red}{nV_1,\qquad nV_2,\qquad\Phi^\dagger nV_1 \Phi,\qquad \Phi nV_2 \Phi^\dagger,\qquad \Phi^\dagger \Phi\Phi^\dagger \Phi}
\end{equation*}
here n can be any positive integer.
\end{frame}
\begin{frame}
    \frametitle{Basic building block -- 3-point}
    From the previous section, we have known that there are only two kinds of 3 point amplitude
    \begin{gather*}
        A[1,2,3^+]=\frac{[23][31]}{[12]},\qquad A[1,2,3^-]=\frac{\avg{23}\!\avg{31}}{\avg{12}}\\
        A[3^+,4^+,5^-]=\frac{[34]^3}{[45][53]},\qquad A[3^-,4^-,5^+]=\frac{\avg{34}^3}{\avg{45}\!\avg{53}}
    \end{gather*}
    By using the 3 point building block, we can construct 4 point color-ordered amplitudes from BCFW recursion relation.
\end{frame}
\begin{frame}
    \frametitle{Gauge boson sector}
    \begin{itemize}
        \item n$ V_1$ or n$V_2$\\
        This part is completely the same as the pure gluon amplitude, so we can directly borrow the
        existing results.
        \begin{equation*}
            \boxed{\text{Parke - Talyor Formula}:\quad A[\cdots,i^-,\cdots,j^-,\cdots]=\frac{\avg{ij}^4}{\avg{12}\!\avg{23}\cdots\avg{n1}}}
        \end{equation*}
        \textcolor{red}{Notice that this formula only applies to MHV amplitudes, although the NMHV can be completely solved.}
    \end{itemize}
\end{frame}
